### 2016-11-14 R/ITHIM.Rmd
Small change to methods paper figure

DALYs <- c(); DALYs.quints <- c();
atVec <- seq(45, 120, length.out = 5)
muNonTravelVec <- c(1, 5, 10)
DTotal <- data.frame()

@@

p <- ggplot(DTotal, aes(x = at,y = -DALYs/1e3, colour = quants))
p + stat_smooth( method = loess) + geom_point() + theme_bw() + scale_y_continuous(name="DALYs Averted Nationwide (Thousands)") + scale_x_continuous(name="Active Transport (minutes/week) (Referent Group)") + facet_grid( . ~ muNonTravel) + theme(axis.text.x  = element_text(angle = 90, vjust = 0.5, size = 8))

>>>>

DALYs <- c(); DALYs.quints <- c();
atVec <- seq(35, 120, length.out = 10)
muNonTravelVec <- c(1, 5, 10)
DTotal <- data.frame()

@@

DTotal <- within(DTotal, muNonTravel <- factor(muNonTravel, levels = c(1,5,10), labels = c("low","medium","high")))
DTotal <- subset(DTotal, quants == "percentiles")

p <- ggplot(DTotal, aes(x = at,y = -DALYs/1e3))#, colour = quants))
p + stat_smooth( method = loess) + geom_point() + theme_bw() + scale_y_continuous(name="DALYs Averted Nationwide (Thousands)") + scale_x_continuous(name="Active Transport (minutes/week) (Referent Group)") + facet_grid( . ~ muNonTravel) + theme(axis.text.x  = element_text(angle = 90, vjust = 0.5, size = 8))
